---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# g4sr

<!-- badges: start -->
<!-- badges: end -->

`g4sr` is an API wrapper for Go4Schools.  It allows you to manage school data.  Authentication is required for all requests.  See your school's administrator for an API key.

## Note

I am in no way affiliated with [Go4Schools](https://www.go4schools.com/).  I am an end user of their [API](https://www.go4schools.com/Documentation/V1/APIDocumentation.html) who happens to use [R](https://www.r-project.org/) quite a lot.

There are a few API calls that are yet to be included.

## Installation

A [CRAN](https://cran.r-project.org/) version is unavailable at this time.  You can install the development version from [GitHub](https://github.com/) by typing the following:

``` r
# install.packages("devtools")
devtools::install_github("afsarchowdhury/g4sr")
```

## Setup

Run `gfs_setup()` and enter your API key in the console.  This is needed before any of the functions can be used.

## Example

To return details of the school and the available academic years:

```{r example, eval=FALSE}
library(g4sr)
gfs_school()
```

To return the school calendar for the academic year 2020:

```{r calendar, eval=FALSE}
my_cal <- gfs_calendar(academicYear = 2020)
my_cal
```
